Decentralised Authoring, Annotations and Notifications for a Read-Write Web with dokieli

### 2017-04-07 index.tex
citing fewer refernces by full title

\par \textbf{Interoperability}: By allowing the application logic to be decoupled from the data, users can switch between applications and personal data storage servers, thereby avoiding a \textit{vendor lock-in}. To achieve maximum interoperability, applications should conform to well-defined Web standards and protocols (rather than properietary software implementations). Dangers of data silos and some example standards to use to decentralise are given in \textit{Socially-aware Cloud Storage}~\cite{ref-2}.

\par \textbf{Separation of concerns}: A \textit{progressive enhancement} strategy to connect the structural, presentational, and behavioural layers allows content and base functionality to be accessible through different media and devices (as described in \textit{Progressive Enhancement and the Future of Web Design}~\cite{ref-3}).

@@

\par \textbf{Web of Trust}: The Web as a collaborative medium makes it possible for people to take responsibility (or be accountable) for their contributions. It should be possible for people to publish, share, and annotate information while ensuring their provenance, authenticity and integrity ~\cite{ref-5,ref-6,ref-7}.

@@

\par \textit{User Interfaces for Semantic Authoring of Textual Content}~\cite{ref-8} gives an overview on relevant related work. A range of quality attributes such as collaboration, interoperability, and scalability, while relevant to our work, we also consider systems and tools on dimensions based on the principles that we have outlined.

@@

\par \textbf{Annotations}: A core feature to facilitate collaboration is the possibility to annotate arbitrary parts of a Web document.
                                    Users can select an entity or a span of text of interest, a context menu is presented to input their annotations along with the choice to select a license for their contribution.
                                    If the user is signed-in with their WebID, and provided they have a personal storage space, dokieli discovers this through their online profile and saves the annotations to that location.
                                    Once the annotation is submitted by the user, dokieli proceeds with three operations: 1) the annotation is requested to be saved at the user’s personal storage, and if it is access controlled, the user will be prompted to authenticate themselves against that server, before the annotation is saved and is assigned its own URL, 2) if the article or any identifiable statement or segment has its own inbox, dokieli sends a notification to the inbox indicating that an annotation was made and with its retrievable location, and accompanying metadata like who created it, date, its license etc., 3) the annotation is fetched from its canonical location, and integrated into the article e.g., in marginalia. If the article has a reference to a public annotation service (a writeable space adhering to \textit{Web Annotation Protocol}~\cite{ref-15}), the user has the option to send a copy of the annotation there as well. In cases where the user does not want to have the canonical copy of the annotation on their server, or if a user does not have write access to a storage, they can use this option to engage with the article.

>>>>

\par \textbf{Interoperability}: By allowing the application logic to be decoupled from the data, users can switch between applications and personal data storage servers, thereby avoiding a \textit{vendor lock-in}. To achieve maximum interoperability, applications should conform to well-defined Web standards and protocols (rather than properietary software implementations). Dangers of data silos and some example standards to use to decentralise are given in~\cite{ref-2}.

\par \textbf{Separation of concerns}: A \textit{progressive enhancement} strategy to connect the structural, presentational, and behavioural layers allows content and base functionality to be accessible through different media and devices (as described in~\cite{ref-3}).

@@

\par \textbf{Web of Trust}: The Web as a collaborative medium makes it possible for people to take responsibility (or be accountable) for their contributions. It should be possible for people to publish, share, and annotate information while ensuring their provenance, authenticity and integrity~\cite{ref-5,ref-6,ref-7}.

@@

\par An overview on relevant related work is given in~\cite{ref-8}. A range of quality attributes such as collaboration, interoperability, and scalability, while relevant to our work, we also consider systems and tools on dimensions based on the principles that we have outlined.

@@

\par \textbf{Annotations}: A core feature to facilitate collaboration is the possibility to annotate arbitrary parts of a Web document.
                                    Users can select an entity or a span of text of interest, a context menu is presented to input their annotations along with the choice to select a license for their contribution.
                                    If the user is signed-in with their WebID, and provided they have a personal storage space, dokieli discovers this through their online profile and saves the annotations to that location.
                                    Once the annotation is submitted by the user, dokieli proceeds with three operations: 1) the annotation is requested to be saved at the user’s personal storage, and if it is access controlled, the user will be prompted to authenticate themselves against that server, before the annotation is saved and is assigned its own URL, 2) if the article or any identifiable statement or segment has its own inbox, dokieli sends a notification to the inbox indicating that an annotation was made and with its retrievable location, and accompanying metadata like who created it, date, its license etc., 3) the annotation is fetched from its canonical location, and integrated into the article e.g., in marginalia. If the article has a reference to a public annotation service (a writeable space adhering to the \textit{Web Annotation Protocol}~\cite{ref-15}), the user has the option to send a copy of the annotation there as well. In cases where the user does not want to have the canonical copy of the annotation on their server, or if a user does not have write access to a storage, they can use this option to engage with the article.
